Enhanced Overall Local Accuracy Framework For Addressing Feature Bias and Data Imbalance in ASD Classification

### 2025-06-05 Paper/BichHao/main.tex
Paper BichHao lan1

José A. Sáez, Julián Luengo, Jerzy Stefanowski, Francisco Herrera ~\cite{b2} introduced SMOTE-IDF, a novel text classification method combining SMOTE oversampling with IDF weighting to tackle class imbalance in textual datasets. Using a Deep Neural Network (DNN) classifier, SMOTE-IDF balances minority class samples while preserving the significance of rare, informative terms. Tested on datasets like 20 Newsgroups, it outperformed traditional oversampling and baseline classifiers in accuracy, precision, recall, and F1-score, highlighting the value of hybrid sampling and feature weighting for imbalanced textual data.

@@

@@

\bibitem{b16} Overall Local Accuracy. Available: \url{https://deslib.readthedocs.io/en/latest/modules/dcs/ola.html}

>>>>

Jose A. Saez, Julian Luengo, Jerzy Stefanowski, Francisco Herrera ~\cite{b2} introduced SMOTE-IDF, a novel text classification method combining SMOTE oversampling with IDF weighting to tackle class imbalance in textual datasets. Using a Deep Neural Network (DNN) classifier, SMOTE-IDF balances minority class samples while preserving the significance of rare, informative terms. Tested on datasets like 20 Newsgroups, it outperformed traditional oversampling and baseline classifiers in accuracy, precision, recall, and F1-score, highlighting the value of hybrid sampling and feature weighting for imbalanced textual data.

@@

\section{Acknowledgment}
We would like to express our sincere gratitude to the University of Information Technology, Vietnam National University Ho Chi Minh City (UIT, VNU-HCM), for their support and for providing the necessary resources throughout this research. This research was supported by The VNUHCM-University of Information Technology’s Scientific Research Support Fund.\\

We also would like to thank experts in the field of psychological health for providing young medical record data and professional documents, who supported the research team to authenticate and consolidate professional knowledge so that the group can achieve the best research results.

@@

% \bibitem{b16} Overall Local Accuracy. Available: \url{https://deslib.readthedocs.io/en/latest/modules/dcs/ola.html}
